Manuscript drafts

### 2020-03-13 datasets/data_preprocessing.nb.Rmd
- update meeting notes - add nagtegaal to preprocessing
introduce bug

```{r}
# data is not public yet

# raw

# asreview
```

@@

## PTSD dataset
```{r}
ptsd <- template 
ptsd["paper", ] <- c(6185, 363, 34) # from flowchart

>>>>

```{r eval = FALSE}
# data is not public yet

# raw --------------------------------------------------------------------------

# asreview ---------------------------------------------------------------------

# remove missing abstracts 
final <- final[final$title != "NA", ]

# remove duplicates (171 duplicates)
final <- final %>%
  distinct(abstract, .keep_all = TRUE)
table(final$inclusion_code)

nrow(final)
final$abstract_included %>% table()
final$included %>% table()

# 
write.csv(final, "data/nagtegaal.csv")

@@

```{r}
nudging["test", ] <- c(1848, 382, 100)
```

## PTSD dataset
```{r}
ptsd <- template 
ptsd["paper", ] <- c(6185, 363, 38) # from flowchart

### 2020-03-13 manuscript/drafts/manuscript.Rmd
introduce bug

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: 
  pdf_document:
    citation_package: biblatex
bibliography: asreview.bib

---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

\newpage
# Introduction
Systematic Reviews (SR's) are booming - but they are a lot of work
Various machien learning tools have been proposed to reduce workload in abstract screening.

- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
- justification 
- background 
- guidance to reader 
- summary/conclusion

-----

@@

@@

- pool unlabeled abstracts $\mathcal{U}$ 
- labeled data set $\mathcal{L}$, 
- instance $x$, label $y$

```{}
while

@@

This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104, ASReview - Smart software for Systematic Reviews.

All simulations were run using through caartesius EINF-156

@@

## Datasets
The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

#### ace 
Cohen et al. collected systematic review datasets from the medical sciences [@Cohen2006]. 
All systematic reviews in this database are on drug efficacy. 
The ace dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.

@@

#### software 
The dataset is retrieved from [@Yu2018a], who collected datasets on literature reviews from the software engineering field. 
This dataset is on fault prediction in software engineering by [@Hall2012].

#### nudging
A review from the behavioural public administration area. 
The SR includes studies on nudging healthcare professionals [@Nagtegaal2019]. 
The data was stored on the Harvard Dataverse [@Nagtegaal2019a].

#### ptsd
A literature review from field of psychology. The SR is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017]. 
The corresponding dataset can be found on the Open Science Framework [...].

#### Wilson
A dataset from the medical sciences [@Appenzeller-Herzog2020]. 
TA review on effectiveness treatments of Wilson disease [@Appenzeller-Herzog2019].

All datasets started with an initial pool of thousands of papers. 
A fraction of these papers where deemed relevant for the SR, with inclusion rates varying from .. to .. (`r table_nums("datasets", display = "cite")`).

@@

We nog have 75 combinations. 
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

@@

@@

<!-- - a model -->
<!-- - a query strategy -->
<!-- - a balance strategy -->
<!-- - a feature extraction strategy -->

@@

### Outcomes 
For each model, 
Several metrics are used to compare performance of different models over datasets,

@@

@@

## Evaluation

@@

# Performance metrics
The goal is twofold: we want to identify all relevant papers, as fast as we can. 
Tradeoff: identifying all relevant papers and reducing workload. 
A good metric to evaluate this is..

@@

>>>>

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output:
  pdf_document:
    keep_tex: yes
    citation_package: biblatex
bibliography: asreview.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

options(tinytex.verbose = TRUE)

@@

\newpage
# Introduction
Systematic Reviews (SR's) are booming - but they are a lot of work
Various machine learning tools have been proposed to reduce workload in abstract screening.

- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
- justification - 
- background 
- guidance to reader 
- summary/conclusion

---

@@

We approach asr as a classification problem: 
All papers obtained in the systematic search form a pool of instances x. 
All instances x need to be classified, e.g. we want to give them a label y. 
all x are now part of U,.
Binary classification, either inclusion or exclusion. 
We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.

By starting of with L, the algorithm utilizes characteristics of X to predict labels in U.

We want to classify the papers in 
Where the whole collection of papers in the systematic search form a pool of instances x, with unknown label y. 
<x,y>. 
```
input: a pool of unlabeled abstracts $\mathcal{U}$ 
oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,

  M = train($\mathcal{L}$)
  query x \isin

```
- pool unlabeled abstracts $\mathcal{U}$ 
- labeled data set $\mathcal{L}$, 
- instance $x$, label $y$

@@

@@

This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.

All simulations were run using through cartesius EINF-156

@@

## Datasets

The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

Cohen et al. collected systematic review datasets from the medical sciences [@Cohen2006]. 
All systematic reviews in this database are on drug efficacy. 
The _ace_ dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.

@@

The _software_ dataset is retrieved from [@Yu2018a], who collected datasets on literature reviews from the software engineering field. 
This dataset is on fault prediction in software engineering by [@Hall2012].

The _nudging_ dataset comes from a review from the behavioural public administration area. 
The SR includes studies on nudging healthcare professionals [@Nagtegaal2019]. 
The data was stored on the Harvard Dataverse [@Nagtegaal2019a].

A literature review from field of psychology, _ptsd_. 
The SR is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017]. 
The corresponding data can be found on the Open Science Framework [...].

_wilson_, a dataset from the medical sciences [@Appenzeller-Herzog2020]. 
TA review on effectiveness treatments of Wilson disease [@Appenzeller-Herzog2019].

All datasets started with an initial pool of thousands of papers. 
A fraction of these papers where deemed relevant for the SR, with inclusion rates around 1-2 percent with one outlier of about 5 percent (`r table_nums("datasets", display = "cite")`).

@@

We now have 75 combinations. 
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

@@

### Statistical analysis 
#### measures
#### comparison over conditions

@@

@@

#### Performance metrics 
For each model, 
Several metrics are used to compare performance of different models over datasets,

@@

The goal is twofold: we want to identify all relevant papers, as fast as we can. 
Tradeoff: identifying all relevant papers and reducing workload. 
A good metric to evaluate this is..

@@

@@

@@

# Appendix C - supercomputer Cartesius

500,000 SBU

Running on Cartesius is charged in System Billing Units (SBUs), and charging is based on the wall clock time of a job. On fat and thin nodes, an SBU is equal to using 1 core for 1 hour (a core hour), or 1 core for 20 minutes on a GPU node. Since compute nodes are allocated exclusively to a single job at a time, you will be charged for all cores on that node - even if you are using less.
